---
title: "Analysis Biblical Proportions"
author: "Batul Arsiwala"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(root.dir = 'C:/Users/Murtaza/Desktop/SCU NOTES/Machine Learning/Data files',echo = TRUE)
```


# Reading the Bible text

*Reading the file and storing each verse in a text array.*
```{r}
text = readLines("C:/Users/Murtaza/Desktop/SCU NOTES/Machine Learning/Data files/ascii_bible.txt")
book_list = list()
vector_verse = c()
in_verse = 0
book = 0
string = ""
for(i in 1:(length(text))){
  if (grepl("\\d\\d\\d:\\d\\d\\d",text[i]) == TRUE){
    if (in_verse == 1){
      vector_verse = c(vector_verse,string)
      book_list[[book]] = c(vector_verse,string)
    }
    string = paste(as.character(book),text[i],sep ="_")
    in_verse = 1
  }else if (text[i] == ""){
      if (in_verse == 1) {
        vector_verse = c(vector_verse,string)
        book_list[[book]] = c(vector_verse,string)
      }
      in_verse = 0
  }else if (grepl("Book\\s*\\d+",text[i])== TRUE){
      book = book+1
  }else{
    text[i] = trimws(text[i],"l")
    string = paste(string,text[i])
  }
}
vector_verse = c(vector_verse,string)
vector_verse[1:20]
```

##How many verses are there in total? 
```{r}
length(vector_verse)
```

##Each verse has the number "CCC:VVV" where CCC is the chapter number and VVV is the verse number.So how many chapters are there? 
```{r}
ch_regex = regexpr("\\d+_\\d\\d\\d:\\d\\d\\d",vector_verse)
chapter_1 = regmatches(vector_verse,ch_regex)
chapter = sapply(strsplit(chapter_1, ":"), "[", 1)
uni_chapter = unique(chapter)
length(uni_chapter) # 1189 chapters
```

## Let's extract an array for the verse numbers, and also one for the verse text.
```{r}
# Extracting array of verse numbers
verse = sapply(strsplit(chapter_1, ":"), "[", 2)

#Extracting array of verse text
verse_text = sub("\\d+_\\d\\d\\d:\\d\\d\\d\\s+", "", vector_verse)
```

## How many unique words are there in the bible?
```{r}
library(tm)
verse_text = tolower(verse_text)
text_corpus = Corpus(VectorSource(verse_text))
temp_verse = tm_map(text_corpus,removePunctuation)
verse_tdm = TermDocumentMatrix(temp_verse,control=list(minWordLength=1))
print(verse_tdm ) # 12646 unique words
```

## Removing all the stopwords. Now how many unique terms are there? 
```{r}
temp_verse_s = tm_map(temp_verse,removeWords,stopwords("english"))
verse_tdm_s = TermDocumentMatrix(temp_verse_s,control=list(minWordLength=1))
print(verse_tdm_s)# 12550 unique words
```

## Now stemming the text, to remove multiplicity of similar words of the same root. 
```{r}
library(SnowballC)
verse_stem = tm_map(temp_verse_s, stemDocument)
```

## How many distinct words are there in the bible, after stemming?
```{r}
verse_tdm_stem = TermDocumentMatrix(verse_stem,control=list(minWordLength=1))
print(verse_tdm_stem)# 9120 distict words
```

## The 50 most common words in the bible:
```{r}
library(slam)
verse_sum = rollup(verse_tdm_stem, 2, na.rm=TRUE, FUN = sum)
verse_sum = as.matrix(verse_sum)
top_words_sum = apply(verse_sum,2,sort,decreasing = TRUE)
top_words_name= rownames(top_words_sum)
top_words_name[1:50]
```

## Wordcloud of the top 100 words in the bible. 
```{r}
library(wordcloud)
wordcloud(top_words_name[1:100],top_words_sum[1:100,])
```
